Life in the canopy: Community trait assessments reveal substantial functional diversity among fern epiphytes

### 2020-02-07 ms/SI.rmd
Output SI to pdf, no docx

---
title: ""
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
- BoldFont=Roboto-Bold.ttf
- ItalicFont=Roboto-Italic.ttf
- BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: none
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: yes
    latex_engine: xelatex
    pandoc_args: [ "--csl", "new-phytologist.csl"]
    includes:
      in_header: new-phytologist.sty
header-includes: 
  - \usepackage{float}
  - \makeatletter\renewcommand*{\fps@figure}{H}\makeatother # Fix position of figs
  - \makeatletter\renewcommand*{\fps@table}{H}\makeatother # Fix position of tables
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: ""
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
- BoldFont=Roboto-Bold.ttf
- ItalicFont=Roboto-Italic.ttf
- BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: none
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "new-phytologist.csl"]
    includes:
      in_header: new-phytologist.sty
header-includes: 
  - \usepackage{float}
  - \makeatletter\renewcommand*{\fps@figure}{H}\makeatother # Fix position of figs
  - \makeatletter\renewcommand*{\fps@table}{H}\makeatother # Fix position of tables
editor_options: 
  chunk_output_type: console
---
